\documentclass{article}
\usepackage[utf8]{inputenc}
%\usepackage[scale=0.8]{geometry}


%----------------------------

\title{Azure DevOps Setup}

%----------------------------


\begin{document}

\maketitle



\section{Create an Azure DevOps Project}
% What did you team do this week? 
% Is your team on schedule? 
%-----------------------------
% Your response goes here
\begin{enumerate}
    \item Login with your St. Thomas email on https://dev.azure.com/ to use your free account
    \item This will give you the option to create a new project, which you can use your team name for. Make the project private
    \item Once it is created, go to the "Overview" tab on the left side of the page. Click "Invite" on the top right of the page and add your team members
    \item Now, you and your team members will have the ability to create sprints, backlog items, and boards. These are all found under the "Boards" tab to the left
    \item If you create a new item or "Issue," you can mouse over it and click the small arrow that appears on the bottom. This will show who the item is assigned to, where you can assign it to yourself or one of your team members (Or you can leave it unassigned and assign team members to smaller tasks on the sprint board, as described in the next step)
    \item If you click the "Sprints" tab, you can see the items you created. You can add individual tasks to be completed by each team member. You can also set iteration dates on the top right of the page to manage when sprints need to be completed by.
\end{enumerate}


\section{Integrate with Microsoft Teams}
% What did your team hope to accomplish that you weren't able to this week? 
%-----------------------------
% Your response goes here. 
\begin{enumerate}
    \item Login with your St. Thomas email on https://teams.microsoft.com/
    \item Click Teams on the left hand side of the page and create a new team
    \item Click Teams again on the left hand side, and then click the three dots in the top corner of your new team that say "More Options" when you mouse over them. Click "Add Member" and add your team members
    \item Open up your team. Under "Posts" you can communicate with your team. Under "Files" you can share files with your team.
    \item Next to Posts and Files, click the "+" to add tabs for your GitHub repositories, Azure DevOps kanban board, etc. Search for them and follow the steps using your St. Thomas or GitHub account to complete the setup
    \item If you choose to integrate with Azure DevOps, you can now click the tab to see your boards, analytics pages, etc. right inside of Microsoft Teams
\end{enumerate}



\end{document}
